### 2015-05-18 writing/SNLI paper/entailment_eval.tex

%
% Baselines
%
\subsection{Baselines}
We evaluate a number of strong baselines on the SNLI corpus.
The first class of baselines use models from the Excitement Open
  Platform (EOP) 
  \cite{pado2014design,magnini2014excitement}
  -- an open source platform for RTE research which
  is distributed alongside a number of RTE pipelines.
We additionally evaluate against a both an unlexicalized and lexicalized
  classifier with straightforward feature sets.
\todo{some meaningful insight from \#s}

@@

\subsection{Sentence embeddings and NLI}

>>>>

Since our goal is to evaluate the quality of the single sentence representations in our model, we train an entailment classifier that has access only to the output of our sentence representation model, and not to any of the word or phrase representations that it used. We encourage future users of this corpus to evaluate their models in this way when possible. Our classifier is simply a stack of three 100d (NONLIN) layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.

\subsection{Baselines}
We evaluate a number of strong baselines on the SNLI corpus.
The first class of baselines use models from the Excitement Open
  Platform (EOP) 
  \cite{pado2014design,magnini2014excitement}
  -- an open source platform for RTE research which
  is distributed alongside a number of RTE pipelines.
We additionally evaluate against a both an unlexicalized and lexicalized
  classifier with straightforward feature sets.
\todo{some meaningful insight from \#s}

@@

\subsection{Sentence embeddings and NLI}\label{sentence-embedding}
\input{model_structure_fig.tex}
